---
title: "Project"
author: "Dereatha Cross & Bijan GURUNG"
date: "4/14/2022"
output: html_document
---

## {.tabset}
### Background

```{r}
install.packages("sf")
install.packages("tidyverse")
library(sf)
library(tidyverse)

flts_pts <- st_read("D:/GEOG 728/Project/LAKE_Mead_Waypoints/LAKE_20200816_to_20210930_Pts_clip_UTM11_comb.shp")
#read the overflights point data of a year 2021/22

head(flts_pts)

glimpse(flts_pts)

#flts_pts_II <- st_read("C:/Users/bijangurung/Desktop/Research/Files_for_GEOG728_final/LAKE_20210716_to_20210731_Pts_clip_UTM11.shp")

#glimpse(flts_pts_II)

#flts_pts_union <- st_union(flts_pts_I, flts_pts_II, by_feature = FALSE)

lake <- st_read("D:/GEOG 728/Project/Lake Western Unit Polygon/LAKE Western Unit Perimeter Polygon.shp")
#read the Lake Mead western perimeter 

head(lake)

glimpse(lake)

lake_buff <- st_buffer(lake, dist = 0.5*1609.34)
#creating a buffer of 0.5 mile around the lake
#1 mile = 1609.34 meters

ggplot()+
  geom_sf(data = lake_buff, aes(fill = UNIT_CODE))

#flts_pts_1 <- flts_pts %>%
#  filter(Alt_AGL_ft %in% (0:5000))
#we only take out the Alt_AGL_ft up to 5,000 ft points

#dim(flts_pts_1)
#dim(flts_pts)

#ggplot()+
#  geom_sf(data = flts_pts_1, size=0.05, alpha=0.5)

#st_crs(flts_pts_1) == st_crs(lake)
st_crs(flts_pts_1)
st_crs(lake)

flts_pts_1 <- flts_pts %>%
  filter(Alt_AGL_ft %in% (4000:4500))
#selecting the waypoints in between 4,000 - 4,500 AGL ft
dim(flts_pts_1)
head(flts_pts_1)

#purposive sampling
flts_pts_2 <- flts_pts_1[1:10000, ]
dim(flts_pts_2)

ggplot()+
  geom_sf(data = lake_buff, aes(fill = UNIT_CODE))+
  geom_sf(data = flts_pts_2, size=0.005, alpha=0.5)






#sampling from the points in flts_pts_1
flts_pts_1_sam <- st_sample(flts_pts_1, 10000, type = "random")
class(flts_pts_1_sam)
head(flts_pts_1_sam)

flts_pts_1_sam <- st_as_sf(flts_pts_1_sam)
class(flts_pts_1_sam)

plot(st_geometry(lake_buff))
plot(flts_pts_1_sam, pch = 16, cex = 0.02, col = "black")
st_crs(flts_pts_1_sam)

install.packages("spatstat")
library(spatstat)

saveRDS(flts_pts_1_sam, file = "flts_pts_fnl.rds")

class(flts_pts_fnl.rds)

flts_pts_3 <- readRDS("flts_pts_fnl.rds")

flts_pts_1_sam_ppp <- as(flts_pts_1_sam, "Spatial")

flts_pts_1_sam <- st_transform(flts_pts_1_sam, crs=st_crs(flts_pts_1))

install.packages("MASS")
library(MASS)

write.matrix(flts_pts_1_sam,file="flts_pts_3.csv", sep = " ")



s_ppp <-as(flts_pts_1_sam, "Spatial")


flts_pts_1_sam <- st_transform(flts_pts_1_sam, crs=st_crs(flts_pts_1))

flts_pts_1_sam <- st_as_sf(flts_pts_1_sam, coords = c("X", "Y"))

flts_pts_1_sam <- st_coordinates(flts_pts_1_sam)

flts_pts_1_sam <- st_sample(flts_pts_1, 10000, type = "random", exact = TRUE)

flts_pts_1_sam <- st_transform(flts_pts_1_sam, st_crs(flts_pts_1))

st_crs(flts_pts_1)

dim(flts_pts_1_sam)
glimpse(flts_pts_1_sam)

head(flts_pts_1)
head(flts_pts_1_sam)
class(flts_pts_1)
class(flts_pts_1_sam)
glimpse(flts_pts_1_sam)

ggplot()+
  geom_sf(data = lake_buff, aes(fill = UNIT_CODE))+
  geom_sf(data = flts_pts_1_sam, size=0.05, alpha=0.5)

st_crs(flts_pts_1_sam) == st_crs(lake_buff)

ggplot()+
  geom_sf(data = lake_buff, aes(fill = UNIT_CODE))+
  geom_sf(data = flts_pts_1, size=0.05, alpha=0.5)
```

## R Markdown


```{r}
install.packages("spatstat")
library(spatstat)

install.packages("basemaps")
library(basemaps)

#data(ext)

#get_maptypes()

#set_defaults(map_service = "mapbox", map_type = "satellite",
#             map_token = "YOUR_MAPTOKEN_IF_NEEDED")

#basemap_plot(ext)

#basemap_mapview(ext)

ggplot()+
  geom_sf(data = lake, aes(fill = UNIT_CODE))+
  geom_sf(data = flts_pts_2, size=0.05, alpha=0.5)

#calculating mean center 
head(flts_pts_2)

xy <- st_coordinates(flts_pts_2)
mc <- apply(xy, 2, mean)
mc

mean_center <- as.data.frame(cbind(mc[1], mc[2]))

ggplot() +
  geom_sf(data = lake_buff) +
  geom_sf(data = flts_pts_2, size=0.05, alpha=0.5) +
  geom_point(data = mean_center, aes(x = V1, y = V2), color = "red", size = 2)


#plot(st_geometry(lake))
#plot(st_geometry(flts_pts_2), add = T, cex=.5, col = "black", pch =16)
#points(cbind(mc[1], mc[2]), pch='*', col='red', cex=5)
```

## Including Plots

You can also embed plots, for example:

```{r}
library(pacman)
p_load(tmap)

tmap_mode("plot")

tm_shape(lake_buff)+
  tm_polygons("UNIT_CODE")+
  #tm_shape(flts_pts_2) + tm_dots(size=0.01, col = "blue")
```

Notes:

Advisory regarding flights over charted National Park Service areas, U.S. Fish and Wildlife Service areas, or U.S. Forest Service areas. All aircraft are requested to maintain a minimum altitude of 2,000 feet above the surface of lands and waters administered by the NPS, UFWS, or USFS Wilderness areas.

Pilots are requested to maintain a minimum altitude of 2,000 feet above the surface of the following: National Parks, Monuments, Seashores, Lakeshores, Recreation Areas and Scenic Riverways administered by the National Park Service, National Wildlife Refuges, Big Game Refuges, Game Ranges and Wildlife Ranges.

```{r}
tmap_mode("view")

tm_basemap("OpenStreetMap")+
  tm_shape(lake_buff) + tm_polygons("UNIT_CODE", alpha = 0.5)+
  tm_shape(flts_pts_2) + tm_dots(size=0.005, col = "blue")
```


```{r}

```

